Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-23 paper/main.tex
write out in full fg_a(v|d)_ger_rms & fg_a(v|d)_ger_lrdiff

\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
these? COH: no clue what to do with that feedback}
% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli
Maximum correlations are found for auditory low-level confounds across stimuli
(\texttt{fg\_a(v|d)\_ger\_rms}, r=.76; \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77),
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.

>>>>

\todo[inline]{SE: "the eight segments": Are you sure, everybody remembered
these? COH: no clue what to do with that feedback}
% we checked correlations
Given the unknown confound structure of the naturalistic stimuli, we inspected
% correlations within stimuli and across stimuli
the correlation of regressors across the eight segments of each stimulus and
also across both stimuli (Fig.~\ref{fig:reg-corr}).
% correlations within each stimulus
The computed Pearson correlation coefficients show only minor correlations of
feature regressors for the same stimulus.
% (highest) correlations across stimuli; \texttt{fg\_a(v|d)\_ger\_rms}, r=.76;
% \texttt{fg\_a(v|d)\_ger\_lrdiff}, r=.77)
Maximum correlations are found for auditory low-level auditory confounds across
stimuli,
% no surprise
which is to be expected, as the audio-description contains the audio track of
the movie plus the additional narrator (Fig. \ref{fig:reg-corr}; correlation
between root mean square volume of both audio tracks, r=.76; correlation between
left-right volume difference of both audio tracks, r=.77).
% encouraged by that we build contrasts (statement)
The observed correlation pattern did not indicate problematic confounds of
nuisance variables and regressors of interest for any of the planned analyses.
